---
title: "House Data Project"
output: html_document
date: '2022-09-21'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load the data:
```{r}
house_data <- read.csv("kc_house_data.csv")
```
Here is what we know about the variables:
id - Unique ID for each home sold
date - Date of the home sale
price - Price of each home sold
bedrooms - Number of bedrooms
bathrooms - Number of bathrooms, where .5 accounts for a room with a toilet but no shower
sqft_living - Square footage of the apartments interior living space
sqft_lot - Square footage of the land space
floors - Number of floors
waterfront - A dummy variable for whether the apartment was overlooking the waterfront or not
view - An index from 0 to 4 of how good the view of the property was
condition - An index from 1 to 5 on the condition of the apartment
grade - An index from 1 to 13, where 1-3 falls short of building construction and design, 7 has an average level of construction and design, and 11-13 have a high quality level of construction and design.
sqft_above - The square footage of the interior housing space that is above ground level
sqft_basement - The square footage of the interior housing space that is below ground level
yr_built - The year the house was initially built
yr_renovated - The year of the house’s last renovation
zipcode - What zipcode area the house is in
lat - Latitude
long - Longitude
sqft_living15 - The square footage of interior housing living space for the nearest 15 neighbors
sqft_lot15 - The square footage of the land lots of the nearest 15 neighbors


Summary of the data set:
```{r}
summary(house_data)
dim(house_data)
```

Load the ggplot library:
```{r}
library(ggplot2)
```

```{r}
ggplot(house_data,
              aes(y = price,
                  x = date)) +
  geom_point(color = "blue", alpha = 0.1, size = 0.5) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) +
  labs(y = "Price ($)",
       x = "Date of Sale",
       title = "Date v Price")
```




Create a visualization:
```{r}
options(scipen = 999999)
g_1 <- ggplot(house_data,
              aes(y = price,
                  x = sqft_living)) +
  geom_point(color = "blue", alpha = 0.1, size = 0.5) +
  theme_bw() +
  geom_smooth(method = "lm") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) +
  labs(y = "Price ($)",
       x = "Living Space (square ft)",
       title = "Living Space v Price")

g_1
```

Visualization 2:
```{r}
g_2 <- ggplot(house_data,
              aes(y = price,
                  x = factor(bathrooms))) +
  geom_boxplot(color = "red", alpha = 0.3) + 
  theme_bw() + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) +
  labs(y = "Price", 
       x = "Number of Bathrooms",
       title = "Price v Bathrooms")

g_2
```

Visualization 3:
```{r}
g_3 <- ggplot(house_data, aes(x = price)) +
  geom_density(fill = "blue", alpha = 0.3) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) +
  labs(x = "Price",
       title = "Density plot of Price")

g_3
```

Visualization 4:
```{r}
library(OneR) #so we can use the bin() function because there are so many years
```


```{r}
t_bins <- bin(house_data$yr_built, nbins = 8, method = "length")

g_4 <- ggplot(house_data,
              aes(y = price,
                  x = t_bins)) +
  geom_point(color = "blue", alpha = 0.3) + 
  theme_bw() + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) +
  labs(y = "Price", 
       x = "Year Built",
       title = "Price vs Year Built")

g_4
```

Log-adjusted price distribution
```{r}
ggplot(house_data, aes(x = log(price))) +
  geom_density(fill = "blue", alpha = 0.3) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) +
  labs(x = "Log(Price)",
       title = "Density plot of Log(Price)")
```


Distribution of Latitude
```{r}
g_lat <- ggplot(house_data, aes(x = lat)) +
  geom_density(fill = "blue", alpha = 0.3) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) +
  labs(x = "Latitude",
       title = "Density plot of Latitudes")

g_lat
```

Distribution of Longitude
```{r}
g_lon <- ggplot(house_data, aes(x = long)) +
  geom_density(fill = "blue", alpha = 0.3) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) +
  labs(x = "Longitude",
       title = "Density plot of Longitudes")

g_lon
```


## Split data into Training and Test
```{r}
RNGkind(sample.kind="Rounding")

set.seed(725385) #seed number from random number generator on Google

train <- sample(c(1:dim(house_data)[1]), dim(house_data)[1]*.8)
train_data <- house_data[train,]
test_data <- house_data[-train,]
```

## Single Tree Model to compare to
```{r}
library(rpart)
single_tree <- rpart(price ~.,
                data = train_data[,3:21])
```

```{r}
#install.packages("Metrics")
library(Metrics)
```

```{r}
single_tree_pred <- predict(single_tree, test_data)
rmse(single_tree_pred, test_data$price)
```
RMSE of $215,936.30 is not good.


## Ensemble Tree Models - Bagging
```{r}
library(randomForest)
```
We will exclude ID because it will have no predictive value, and exclude date because all sales are within a year so it is unlikely to be significant
```{r}
set.seed(725385) #seed number from random number generator on Google

bag_mod <- randomForest(price ~.,
                data = train_data[,3:21],
                mtry = 18, # Set mtry to number of variables 
                ntree = 200)
bag_mod
```
87.83% variation explained is pretty good

Predict using bagging model and get the RMSE:
```{r}
bag_preds <- predict(bag_mod, test_data)
rmse(bag_preds, test_data$price)
```
This is not a very accurate model. $132,982.50 root mean square error on predictions of test data.

Let's take a look at the RMSE
```{r}
RMSE <- sqrt(bag_mod$mse) # Extract MSE
plot_dat <- cbind.data.frame(rep(1:length(RMSE)), RMSE) # Create plot data
names(plot_dat) <- c("trees", "RMSE") # Name plot data

# Plot oob error
g_5 <- ggplot(plot_dat, aes(x = trees, y = RMSE)) + # Set x as trees and y as error
  geom_point(alpha = 0.5, color = "blue") + # Select geom point
  geom_smooth() + # Add smoothing line
  theme_bw() + # Set theme
  theme(panel.grid.major = element_blank(), # Remove grid
        panel.grid.minor = element_blank(), # Remove grid
        panel.border = element_blank(), # Remove grid
        panel.background = element_blank()) + # Remove grid 
  labs(x = "Number of Trees", title = "RMSE v Number of Trees",
       y = "RMSE")  # Set labels
g_5 # Print plot
```
It appears 200 trees was more than enough since the MSE evened out after about 70 trees.



Let's tune this model.
```{r}
trees <- c(25, 50, 100, 200) # Create vector of possible tree sizes
nodesize <- c(1, 10, 25, 50, 100) # Create vector of possible node sizes

params <- expand.grid(trees, nodesize) # Expand grid to get data frame of parameter combinations
names(params) <- c("trees", "nodesize") # Name parameter data frame
res_vec <- rep(NA, nrow(params)) # Create vector to store accuracy results

for(i in 1:nrow(params)){ # For each set of parameters
  set.seed(725385) # Set seed for reproducability
  mod <- randomForest(price ~. , # Set formula
                      data=train_data[,3:21],# Set data
                      mtry = 18, # Set number of variables
                      importance = FALSE,
                      ntree = params$trees[i], # Set number of trees
                      nodesize = params$nodesize[i]) # Set node size
  res_vec[i] <- mod$mse[length(mod$mse)] # MSE values
}
```

```{r}
summary(res_vec)
RMSE <- sqrt(res_vec)
summary(RMSE)
```

```{r}
res_db <- cbind.data.frame(params, RMSE) # Join parameters and accuracy results
names(res_db)[3] <- "RMSE" # Name accuracy results column
res_db
```

```{r}
res_db$trees <- as.factor(res_db$trees) # Convert tree number to factor for plotting
res_db$nodesize <- as.factor(res_db$nodesize) # Convert node size to factor for plotting
g_6 <- ggplot(res_db, aes(y = trees, x = nodesize, fill = RMSE)) + # set aesthetics
  geom_tile() + # Use geom_tile for heatmap
  theme_bw() + # Set theme
  scale_fill_gradient2(low = "blue", # Choose low color
    mid = "white", # Choose mid color
    high = "red", # Choose high color
    midpoint = mean(res_db$RMSE), # Choose mid point
    space = "Lab", 
    na.value ="grey", # Choose NA value
    guide = "colourbar", # Set color bar
    aesthetics = "fill") + # Select aesthetics to apply
  labs(x = "Node Size", y = "Number of Trees", fill = "RMSE") # Set labels
g_6 # Generate plot
```

```{r}
res_db[which.min(res_db$RMSE),]
```

Let's remove house prices over $2,000,000
```{r}
set.seed(725385) #seed number from random number generator on Google
train_no_outlier <- train_data[train_data$price < 2000000,]
bag_mod2 <- randomForest(price ~.,
                data = train_no_outlier[,3:21],
                mtry = 18,
                ntree = 200)
bag_mod2
```

```{r}
bag_preds2 <- predict(bag_mod2, test_data)
rmse(bag_preds2, test_data$price)
```


```{r}
RMSE2 <- sqrt(bag_mod2$mse) # Extract MSE
plot_dat2 <- cbind.data.frame(rep(1:length(RMSE2)), RMSE2) # Create plot data
names(plot_dat2) <- c("trees", "RMSE") # Name plot data

# Plot oob error
g_7 <- ggplot(plot_dat2, aes(x = trees, y = RMSE)) + # Set x as trees and y as error
  geom_point(alpha = 0.5, color = "blue") + # Select geom point
  geom_smooth() + # Add smoothing line
  theme_bw() + # Set theme
  theme(panel.grid.major = element_blank(), # Remove grid
        panel.grid.minor = element_blank(), # Remove grid
        panel.border = element_blank(), # Remove grid
        panel.background = element_blank()) + # Remove grid 
  labs(x = "Number of Trees", title = "RMSE v Number of Trees",
       y = "RMSE")  # Set labels
g_7 # Print plot
```
This made the predictive power of the model worse.

## Cross-Validated Bagging Model
```{r}
set.seed(725385)
# Create cross-validation index
cv_ind <- sample(1:5, nrow(train_data), replace = TRUE )

# Create accuracy store
cv_RMSE <- rep(NA, 5)
for(i in 1:5){ # For 1 to 5
  cv_train <- train_data[cv_ind != i ,c(3:21)] # Create training data
  cv_test <- train_data[cv_ind == i,  c(3:21)] # Create test data

  bag_mod_3 <- randomForest(price ~., # Set tree formula
                data = cv_train, # Set dataset
                mtry = 18, # set number of variables to use
                ntree = 200, # Set number of trees to generate
                nodesize = 1) # Set node size
  bag_preds_3 <- predict(bag_mod_3, cv_test) # Create test data predictions

  rmse <- rmse(bag_preds_3, cv_test$price)
  cv_RMSE[i] <- rmse # RMSE values
}

# Print cross validated accuracy scores
cv_RMSE
```
```{r}
mean(cv_RMSE)
```
This is a slight improvement from the original bagging model RMSE of 132,982.50 to 127,337.50 for the cross-validated model, however, 127,000 is still a lot of error. This is still a large improvement from the 215,936.30 RMSE of the single tree model.

## Important Variables
```{r}
varImpPlot(bag_mod, type =2, n.var = 10)
varImpPlot(bag_mod2, type =2, n.var = 10)
varImpPlot(bag_mod_3, type =2, n.var = 10)
```

## Ensemble Tree Models - Bagging with log(price)

```{r}
set.seed(725385) #seed number from random number generator on Google

bag_mod_log <- randomForest(log(price) ~.,
                data = train_data[,3:21],
                mtry = 18, 
                ntree = 200)
bag_mod_log
```
88.41% variation explained is pretty good

Predict using bagging model and get the RMSE:
```{r}
bag_preds_log <- predict(bag_mod_log, test_data)
preds_log_adj <- exp(bag_preds_log)
rmse(preds_log_adj, test_data$price)
```
This is not a very accurate model. $127,769.1 root mean square error on predictions of test data.
This is a slightly better model than the original ensemble.


## Log-adjusted ensemble using parameters from before
```{r}
mod_log <- randomForest(log(price) ~. ,
                      data=train_data[,3:21],
                      mtry = 18,
                      importance = FALSE,
                      ntree = 200,
                      nodesize = 1)
mod_log
```
88.39% variation explained is slightly worse than the first log-adjusted model.

Predict using bagging model and get the RMSE:
```{r}
bag_preds_log2 <- predict(mod_log, test_data)
preds_log_adj2 <- exp(bag_preds_log2)
rmse(preds_log_adj2, test_data$price)
```
129,419.50 RMSE is worse than the previous 2 models


```{r}
varImpPlot(bag_mod_log, type =2, n.var = 10)
varImpPlot(mod_log, type =2, n.var = 10)
```


## Refined Variables

Lastly, lets try removing latitude and longitude since they are very important but are almost the same for each house since the houses are all in the same general area

```{r}
train_data_2 <- train_data[,-c(18:19)]
test_data_2 <- test_data[,-c(18:19)]
```


```{r}
mod_no_lat_lon <- randomForest(price ~. ,
                      data=train_data_2[,3:19],# Set data
                      mtry = 16, # Set number of variables
                      importance = FALSE,
                      ntree = 200, # Set number of trees
                      nodesize = 1) # Set node size
```

Predict using bagging model and get the RMSE:
```{r}
bag_preds_no_lat_lon <- predict(mod_no_lat_lon, test_data_2)
rmse(bag_preds_no_lat_lon, test_data_2$price)
```
This model became much worse without latitude and longitude included, indicating that differences of just a few miles can have strong impacts on the prices of homes.


