---
title: "Network Analysis"
output: github_document
date: "2022-11-30"
---

% Web 34 Chesapeake Bay Mesohaline Network; D. Baird; Umcees Ref No. XXX-86; MGC/M2/SUM 1
% from datall.zip from http://www.cbl.cees.edu/~ulan/ntwk/network.html
% Chesapeake Bay mesohaline ecosystem. Summer carbon flows.
% Baird, D. and R.E. Ulanowicz. 1989. The seasonal dynamics of the
% Chesapeake Bay ecosystem. Ecol. Monogr. 59: 329-364.
% transformed from SCOR format by Scor2net 15.7.2003
*partition ECO types / chesapeake

```{r}
Chesapeake <- read.table("Chesapeake.paj", quote="\"", comment.char="")
nodelist <- read.csv("Chesapeake Nodelist.csv")
```


```{r}
library(igraph)
library(ggraph)

net <- graph_from_data_frame(Chesapeake, directed = T, vertices = union(unique(Chesapeake$V2), unique(Chesapeake$V1)))
net <- simplify(net, remove.multiple = F, remove.loops = T)
```

```{r}
#new_net <- net %>%
 # delete_vertices(c(34, 35, 36, 37, 38, 39)) 
#ggraph(new_net) +
 # geom_edge_link0() +
 # geom_node_point()

#subset(Chesapeake, V1 = "1:33")
#subset(Chesapeake, V2 = 1:33)
#filter(Chesapeake, V1 == 13)
Chesapeake_1 <- Chesapeake[Chesapeake$V1 %in% 1:33, ]    # Subset data frame
Chesapeake_2 <- Chesapeake_1[Chesapeake_1$V2 %in% 1:33, ]
Chesapeake_2

ggraph(Chesapeake_2) +
  geom_edge_link(color = "black", alpha = 0.3) +
  geom_node_point(color = "blue") +
  theme_graph()

#Chesapeake_no_blue_crab <- Chesapeake_2[Chesapeake_2$V1 %in% 1:18 | 20:33, ]
#Chesapeake_no_blue_crab_final <- Chesapeake_no_blue_crab[Chesapeake_no_blue_crab$V1 %in% 1:18 | 20:33, ]
#Chesapeake_no_blue_crab_final

Chesapeake_nbc <- subset(Chesapeake_2, V1 != 19)
Chesapeake_nbc <- subset(Chesapeake_2, V2 != 19)
Chesapeake_nbc
```

```{r}
net <- graph_from_data_frame(Chesapeake_2, directed = T, vertices = union(unique(Chesapeake_2$V2), unique(Chesapeake_2$V1)))
net <- simplify(net, remove.multiple = F, remove.loops = T)
#GOOD 
ggraph(net) +
  geom_edge_link(color = "black", alpha = 0.3) +
  geom_node_point(color = "blue") +
  theme_graph()

#GOOD WITH DEGREE
ggraph(net) +
  geom_edge_link(color = "black", alpha = 0.3) +
  geom_node_point(color = "blue", size = igraph::degree(net, mode = "all")) +
  theme_graph()


plot(net, edge.arrow.size=.4, edge.curved=.1) 
```

```{r}
inc.edges <- incident(net, V(net)["19"], mode="all")
# Set colors to plot the selected edges.
ecol <- rep("gray80", ecount(net))
ecol[inc.edges] <- "orange"
vcol <- rep("grey40", vcount(net))
vcol[V(net)$V1 == "19"] <- "gold"
plot(net, vertex.color=vcol, edge.color=ecol, edge.width=2)
```



Network containing blue crab 
```{r}
library(igraph)
#setwd("YOUR WORKING DIRECTORY HERE")


# igraph's sir function does require the network to be simple (no loops or multiplex ties)
# Simplified graphs do not have any loops or multiplex ties. 
is.simple(net) #TRUE, so it's fine
# igraph's sir function *also* needs the graph to be undirected
is_directed(net) #TRUE, so we need to change it
un_net <- as.undirected(net)
is_directed(un_net) #FALSE, good

# The igraph function uses different arguments than EpiModel
# beta is the rate of infection, gamma is the rate of recovery
sir52 <- sir(graph = un_net, beta = 5, gamma = 2) 
class(sir52) # output is a sir object/list. Use indexing to look inside. 
invisible(sir52) # lots of pieces
sir52[[1]] # the first simulation
sir52[[1]]$times # times of events
sir52[[1]]$NS # number susceptible
sir52[[1]]$NI # number infected
sir52[[1]]$NR # number recovered
#plot(sir52) # shows all simulations at once
plot(sir52, comp = "NS")
plot(sir52, comp = "NI")
plot(sir52, comp = "NR")
```
No Blue crab code
```{r}
net_nbc <- graph_from_data_frame(Chesapeake_nbc, directed = T, vertices = union(unique(Chesapeake_nbc$V2), unique(Chesapeake_nbc$V1)))
net_nbc <- simplify(net_nbc, remove.multiple = F, remove.loops = T)
```

```{r}
dim(Chesapeake_2)
dim(Chesapeake_nbc)
```

NO BLUE CRAB NETWORK
```{r}
#GOOD 
ggraph(net_nbc) +
  geom_edge_link(color = "black", alpha = 0.3) +
  geom_node_point(color = "blue") +
  theme_graph()

ggraph(net_nbc) +
  geom_edge_link(color = "black", alpha = 0.3) +
  geom_node_point(color = "blue", alpha = 0.8, size = igraph::degree(net, mode = "all")) +
  theme_graph()

deg <- degree(net_nbc)
V(net_nbc)$size <- deg*3
```
NO BLUE CRAB CONTAGION 
```{r}
library(igraph)
#setwd("YOUR WORKING DIRECTORY HERE")


# igraph's sir function does require the network to be simple (no loops or multiplex ties)
# Simplified graphs do not have any loops or multiplex ties. 
is.simple(net_nbc) #TRUE, so it's fine
# igraph's sir function *also* needs the graph to be undirected
is_directed(net_nbc) #TRUE, so we need to change it
un_net <- as.undirected(net_nbc)
is_directed(un_net) #FALSE, good

# The igraph function uses different arguments than EpiModel
# beta is the rate of infection, gamma is the rate of recovery
sir52 <- sir(graph = un_net, beta = 5, gamma = 2) 
class(sir52) # output is a sir object/list. Use indexing to look inside. 
invisible(sir52) # lots of pieces
sir52[[1]] # the first simulation
sir52[[1]]$times # times of events
sir52[[1]]$NS # number susceptible
sir52[[1]]$NI # number infected
sir52[[1]]$NR # number recovered
plot(sir52) # shows all simulations at once
```

```{r}
plot(sir52, comp = "NS")
plot(sir52, comp = "NI")
plot(sir52, comp = "NR")
```

```{r}
#vertex.label=V(net)$media
net.bg <- net
plot(net.bg, layout = layout_randomly)

l <- layout_in_circle(net.bg)
plot(net.bg, layout=l, edge.arrow.size =.1)
```

```{r}
library(plyr)
library(tidyr)
library(statnet)
library(ggplot2)
library(ggnetwork)
library(dplyr)
library(igraph) 
library(igraphdata)
library(ggraph)
library(gplots)
```

create net_sna object
```{r}
net_sna <- network(Chesapeake_2, matrix.type = "edgelist", directed = T, loops = TRUE)
net_sna
```

Run a CUG Test
```{r}
Cug_Size <- cug.test(net_sna, gtrans, cmode="size")
plot(Cug_Size) 
```

Find the strong cut-set of the graph
```{r}
cp <- cutpoints(net_sna, mode = "digraph")
cp
```

Calculate the cluster-louvain algorithm on this graph, find number of communities plus mod
```{r}
un_net <- graph_from_data_frame(Chesapeake_2, directed = F, vertices = nodelist)
clv <- cluster_louvain(un_net, weights = NULL)
length(clv)
modularity(clv) 
```

Calculate spin-glass, find number of communities plus mod
```{r}
sgc <- cluster_spinglass(net)
length(sgc)
modularity(sgc) 
```

Increase resolution parameter, how does it affect number of communities and modularity
```{r}
clv_5 <- cluster_louvain(un_net, resolution = 0.5)
length(clv_5)
modularity(clv_5)
```

Plot Communities
```{r}
library(igraph) 
set.seed(12345)
E(net)$weight <- sample(x = 1:10, size = ecount(net), replace = TRUE)
cl <- cluster_louvain(un_net)
# V(net)$name <- membership(cl)
x <- as_edgelist(net, names = T)
V(net)$name <- 1:vcount(net)
E(net)[x[,1] != x[,2]]
 E(net)$color <- ifelse(x[,1] != x[,2], "red", "blue")
 plot(net, edge.color = E(net)$color)
 plot(cl, un_net)
```


Centrality Measures

Degree Measures
```{r}
# DEGREE
deg <- igraph::degree(net)
deg

ggraph(net) + 
  geom_edge_link0(color = "grey") +
  geom_node_point(color = "blue", 
                  size = V(net)$size <- igraph::degree(net, mode = "all")/3) +
  ggnetwork::theme_blank()


# IN DEGREE
deg_in <- igraph::degree(net, mode = "in")
deg_in

ggraph(net) + 
  geom_edge_link(color = "grey", 
                 arrow = arrow(length = unit(2, 'mm')), 
                 start_cap = circle(2, 'mm'),
                 end_cap = circle(2, 'mm')) + 
  geom_node_point(color = "blue", 
                  size = igraph::degree(net, mode = "in")) +
#  geom_node_text(aes(label = name)) +
  ggnetwork::theme_blank()


# OUT DEGREE
deg_out <- igraph::degree(net, mode = "out")
deg_out

ggraph(net) + 
  geom_edge_link(color = "grey", 
                 arrow = arrow(length = unit(2, 'mm')), 
                 start_cap = circle(2, 'mm'),
                 end_cap = circle(2, 'mm')) +
  geom_node_point(color = "blue", 
                  size = V(net)$size <- igraph::degree(net, mode = "out")) + 
#  geom_node_text(aes(label = name)) +
  ggnetwork::theme_blank()
```

Closeness Measures
```{r}
# CLOSENESS
close <- igraph::closeness(net)
close

is_directed(net)
un_net <- as.undirected(net)

ggraph(un_net) + 
  geom_edge_link0(color = "grey") +
  geom_node_point(color = "blue", 
                  size = igraph::closeness(un_net)*250) +
  ggnetwork::theme_blank()


# IN CLOSENESS
close_in <- igraph::closeness(net, mode = "in")
close_in

ggraph(net) + 
  geom_edge_link0(color = "grey", 
                  arrow = arrow(length = unit(2, 'mm')), 
                  start_cap = circle(2, 'mm'),
                  end_cap = circle(2, 'mm')) +
  geom_node_point(color = "blue", 
                  size = igraph::closeness(net, mode = "in")*10) +
#  geom_node_text(aes(label = name)) +
  ggnetwork::theme_blank()


# OUT CLOSENESS
close_out <- igraph::closeness(net, mode = "out")
close_out

ggraph(net) + 
  geom_edge_link0(color = "grey", 
                  arrow = arrow(length = unit(2, 'mm')), 
                  start_cap = circle(2, 'mm'),
                  end_cap = circle(2, 'mm')) +
  geom_node_point(color = "blue", 
                  size = igraph::closeness(net, mode = "out")*10) +
  ggnetwork::theme_blank()
```

Betweenness
```{r}
bet_d <- igraph::betweenness(net, directed = T)
bet_d

ggraph(net) + 
  geom_edge_link0(color = "grey") + 
  geom_node_point(color = "blue", 
                  size = igraph::betweenness(net, directed = T)/5) +
#  geom_node_text(aes(label = name)) +
  ggnetwork::theme_blank()
```

Edge Betweenness
```{r}
eb_n <- edge.betweenness(net, directed = T)
eb_n

ggraph(net) + 
  geom_edge_link0(color = "grey", 
                  aes(width = edge.betweenness(net, directed = T))) +
  scale_edge_width(range = c(0.15, 1)) +
  geom_node_point(color = "blue") +
  ggnetwork::theme_blank() + theme(legend.position = "none")
```


ERGM Models
```{r}
Chesapeake <- read.table("Chesapeake.paj", quote="\"", comment.char="")
Chesapeake_1 <- Chesapeake[Chesapeake$V1 %in% 1:33, ]
Chesapeake_2 <- Chesapeake_1[Chesapeake_1$V2 %in% 1:33, ]
Chesapeake_2
```

Data Cleaning: Removing the self-loop on node 19
```{r}
Chesapeake_2[59,]
Chesapeake_2 <- Chesapeake_2[-(59),]
Chesapeake_2
```

```{r}
net

ggraph(net) +
  geom_edge_link(color = "black", alpha = 0.3) +
  geom_node_point(color = "blue") +
  theme_graph()
```


```{r}
library(ergm)
library(ggraph)
library(statnet)
```

```{r}
net_sna <- network(Chesapeake_2, matrix.type = "edgelist", directed = T, loops = FALSE)
net_sna

model1 <- ergm(net_sna ~ edges)
```

```{r}
ggraph(net_sna) +
  geom_edge_link0(color = "black") +
  geom_node_point(color = "#DFE6EB") +
  ggnetwork::theme_blank()
```

ERGM
```{r}
model1 <- ergm(net_sna ~ edges)

summary(model1)
```

```{r}
summary(net_sna ~ edges)
```

prob
```{r}
mod_sum <- summary(model1)
mod_sum #log-odds
exp(coef(mod_sum)[1]) #odds
beta <- coef(mod_sum)[1]
beta
```


```{r}
prob <- exp(beta)/(1+exp(beta))
prob
plogis(beta)
plogis(coef(model1)[['edges']])
```
the probability of forming a tie with someone else at random is 6.7%


```{r}
gden(net_sna)
```

simulation
```{r}
set.seed(123)
ergm1 <- simulate(model1)
ggraph(ergm1) +
  geom_edge_link0(color = "black") +
  geom_node_point(color = "#DFE6EB") +
  ggnetwork::theme_blank()
```

```{r}
  # gof####
model1_gof <- gof(model1) 
model1_gof
# We use GOF to see if our simulated network is like our real network
# If the fit is poor, we need to re-specify
```

```{r}
plot(model1_gof) 
```

Compare to our model
```{r}
model1_gof_model = gof(model1, GOF = ~ model)
model1_gof_model
```


```{r}
gof(model1, GOF = ~ triadcensus)
```


Adding Reciprocity
```{r}
model2 <- ergm(net_sna ~ edges + mutual)

summary(model2)
```

```{r}
coef(model2)
plogis(coef(model2)[['edges']] + coef(model2)[['mutual']])
```
There are no mutual ties since this is a food web so each organism is either predator or prey to another organism, but cannot be both.


Adding In Degree
```{r}
network::set.vertex.attribute(net_sna, "indegree", sna::degree(net_sna, cmode = "indegree"))
net_sna
```

```{r}
model3 <- ergm(net_sna ~ edges + nodeicov("indegree"))

summary(model3)
```

```{r}
plogis(coef(model3)[['edges']] + coef(model3)[['nodeicov.indegree']])
```

```{r}
set.seed(123)
ergm3 <- simulate(model3)
ggraph(ergm3) +
  geom_edge_link0(color = "black") +
  geom_node_point(color = "#DFE6EB") +
  ggnetwork::theme_blank()

plot(gof(model3))
```


Adding Transitivity
```{r}
model4 <- ergm(net_sna ~ edges + nodeicov("indegree") + gwesp, 
                 control = control.ergm(MCMLE.maxit=10))

summary(model4)
```


```{r}
plogis(coef(model4)[['edges']] + coef(model4)[['nodeicov.indegree']] + 
  coef(model4)[['gwesp.OTP']] + coef(model4)[['gwesp.OTP.decay']])
```


```{r}
set.seed(123)

ergm4 <- simulate(model4)

ggraph(ergm4) +
  geom_edge_link0(color = "black") +
  geom_node_point(color = "#DFE6EB") +
  ggnetwork::theme_blank()

plot(gof(model4))
```
